Gozde and Liora Replication Code

### 2015-04-10 Gozde-Liora-Replication-Code.Rmd
Fixing typo from: deleting base R graphs, adding an explanation of how we wrote code for our figures to be reuseable for different variables of interest in other figures

# Figure 1 (Conditonal Effects of Unemployment and Immigration)
![Figure 1](figures/fig1.png)
```{r}
library(msm)
asy <- seq(from = -.98, to = 4.46, by = .01) # vector with possible values for asylumseekers
variable <- asy # to standardize the code
slopes <- model$coef$fixed[17] + model$coef$fixed[36] * asy # Estimated slopes based on estimated coefficients of unemployment (17) and unemployment x immigration (36)
estmean <- model$coef$fixed # Estimated means for each variable 
var <- vcov(model) # Estimated variances
se <- rep(NA, length(asy))

@@

# Creating the first graph in base R 
par(mfrow = c(2, 1))
plot(variable, slopes, type = "l", lty = 1, ylim = c(-.2, .2), xlim = c(-2, 4), ylab = "Effect: Unemployment", xlab = "Asylumseekers", main = "The Conditional Effects of Unemployment and Immigration")
points(variable, upper, type = "l", lty = 2)
points(variable, lower, type = "l", lty = 2)
points(variable, rep(0, length(variable)), type = "l", col = "black")

# Creating the same graph with ggplot - much better looking.

@@

# Creating second part of the figure in base R

plot(variable, slopes, type = "l", lty = 1, ylim=c(-.4, .6), xlim=c(-5, 15), ylab= "Effect: Asylum seekers", xlab = "Unemployment", main = "The Conditional Effects of Unemployment and Immigration")
points(variable, upper, type = "l", lty = 2)
points(variable, lower, type = "l", lty = 2)
points(variable, rep(0, length(variable)), type = "l", col = "black")

# Creating the same graph with ggplot:

@@

# Creating the first graph in base R

plot(variable, slopes, type = "l", lty = 1, ylim=c(-.02, .03), xlim=c(-5, 20), ylab= "Effect: Variance", xlab = "Salience", main = "The Conditional Effects of Salience and Variance")
points(variable, upper, type = "l", lty = 2)
points(variable, lower, type = "l", lty = 2)
points(variable, rep(0, length(variable)), type = "l", col = "black")

# Creating the same graph with ggplot:

@@

# Creating the second graph in base R 
par(mfrow = c(1,1))
plot(variable, slopes, type = "l", lty = 1, ylim = c(-.05, .2), xlim = c(-50, 150), ylab = "Effect: Saliance", xlab = "Variance")
points(variable, upper, type = "l", lty = 2)
points(variable, lower, type = "l", lty = 2)
points(variable, rep(0, length(variable)), type = "l", col = "black")

# Creating the same graph with ggplot:

>>>>

# Figure 1 (Conditonal Effects of Unemployment and Immigration)
![Figure 1](figures/fig1.png)
```{r}
library(msm)
asy <- seq(from = -.98, to = 4.46, by = .01) # vector with possible values for asylumseekers
variable <- asy # identifying "asy" as the variable of interest so that the remaining code can be reused in the next graph with a different variable of interest specified
slopes <- model$coef$fixed[17] + model$coef$fixed[36] * asy # Estimated slopes based on estimated coefficients of unemployment (17) and unemployment x immigration (36)
estmean <- model$coef$fixed # Estimated means for each variable 
var <- vcov(model) # Estimated variances
se <- rep(NA, length(asy))

@@

# Creating the first graph with ggplot

@@

# Creating the second graph with ggplot:

@@

# Creating the first graph with ggplot:

@@

# Creating the second graph with ggplot:
